% Compile with: xelatex CV.tex
% Requires: Fonts: Garamond Premier Pro, DejaVu Sans Mono
\documentclass[10pt,a4paper]{article}
\usepackage{doi}
\usepackage{url}
\usepackage{amsmath}
\usepackage[no-math]{fontspec}
\setmainfont[Mapping=tex-text, Contextuals=Alternate,Numbers=OldStyle]{Garamond Premier Pro}
\setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{geometry}

\definecolor{pastelred}{RGB}{200,80,80}
\definecolor{pastelgreen}{RGB}{0,150,80}

% Set your name here
\def\name{Christopher J. Billington}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = pastelred,
  pdfauthor = {\name},
  pdfkeywords = {physics, atomic physics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  Building 216 \\
  National Institute of Standards and Technology \\
  100 Bureau drive \\
  Gaithersburg, Maryland
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Office: +1 (301) 975 4266 \\
  Mobile: +1 (857) 763 8547 \\
  Email: \href{mailto:cbil@umd.edu}{cbil@umd.edu} \\
\end{minipage}

\section*{Education}

\begin{itemize}

  \item Doctor of Philosophy, Monash University, completed 2018.
    \begin{itemize}
    \item \textit{Thesis title:}
      State-dependent force in cold quantum gases
    \end{itemize}
    
  \item Bachelor of Science Advanced with Honours, Monash University, completed 2010.
    \begin{itemize}
    \item \textit{Majors:}
      Physics, Mathematics.
    \item \textit{Honours in:}
      Physics.
    \item \textit{Honours grade:} 91 (\textsc{H}1)
    \end{itemize}
    
  
\end{itemize}

\section*{Research}
\begin{itemize}

\item{Postdoctoral researcher at the Joint Quantum Institute, NIST/University of Maryland, October 2016--present}
    \begin{itemize}
      \item \textit{Research area:}
      Experimental cold atom physics, experiment control systems
      \item \textit{Principal Investigator:}
      Prof.~Ian Spielman
    \end{itemize}

\item{Visiting researcher at the Joint Quantum Institute, NIST/University of Maryland, August--December 2014}
    \begin{itemize}
      \item \textit{Research area:}
      Experiment control systems, experimental cold atom physics
      \item \textit{Supervisor:}
      Prof.~Ian Spielman
    \end{itemize}

\item{Exchange student at the Physikalisches Institut, Universität Tübingen, March–September 2013}
    \begin{itemize}
      \item \textit{Research area:}
      Experiment control systems, experimental cold atom physics
      \item \textit{Supervisor:}
      Prof.~József Fortágh
    \end{itemize}
    
\item{PhD candidature, Monash University School of Physics, February 2011--June 2018.}
    \begin{itemize}
      \item \textit{Thesis title:}
      State-dependent forces in cold quantum gases
      \item\textit{Supervisors:}
      Prof.~Kris Helmerson, Dr.~Lincoln Turner, and Dr.~Russell Anderson.
    \end{itemize}
\item Summer employment, dual-species Bose--Einstein condensation lab, Monash University, summer 2010--2011.
\item PHS4100 physics thesis project, Monash University, 2010
    \begin{itemize}
      \item \textit{Thesis title:}
      Particle Velocimetry of Vortices in Bose--Einstein Condensates
      \item\textit{Supervisor:}
      Prof.~Kris Helmerson.
    \end{itemize}
\item Summer employment, dual-species Bose--Einstein condensation lab, Monash University, summer 2009--2010.
\item PHS3360 physics project unit, Monash University, summer 2009--2010
    \begin{itemize}
      \item \textit{Project title:}
      Condensed atoms as tracer particles in two component Bose--Einstein condensates
      \item\textit{Supervisor:}
      Prof. Kris Helmerson.
    \end{itemize}
\item PHS3350 physics project unit, Monash University, 2009
    \begin{itemize}
      \item \textit{Project title:}
      Bose--Einstein condensates in `Magic' optical traps
      \item\textit{Supervisors:}
      Dr.~Lincoln Turner, Prof.~Kris Helmerson.
    \end{itemize}    
\item Summer research scholarship, Australian National University Research School of Astronomy and Astrophysics, summer 2008--2009.
    \begin{itemize}
      \item \textit{Project title:}
      Lunar orbital evolution: Causes and geological implications.
      \item\textit{Supervisor:}
      Dr. Charley Lineweaver.
    \end{itemize}

\end{itemize}


\section*{Teaching Experience}

\begin{itemize}
\item Demonstrating in third year undergraduate teaching labs, Monash University School of Physics, semester 1, 2014.
\item Demonstrating in second year undergraduate teaching labs, Monash University School of Physics, semester 2, 2013.
\item Demonstrating in third year undergraduate teaching labs, Monash University School of Physics, semesters 1 and 2, 2012.
\item Demonstrating in second year undergraduate teaching labs, Monash University School of Physics, semesters 1 and 2, 2010.
\end{itemize}

\section*{Conference Presentations}

\begin{itemize}


\item 8th annual Conference on Optics, Atoms and Laser Applications, contributed talk, December 2015.
   \begin{itemize}
      \item \textit{Talk title:}
      Reproduction of Stern--Gerlach-like behavior in semiclassical models using hidden variables
      \item\textit{Authors:}
      C. J. Billington, C. Watkins, F. Pollock, R. P. Anderson, L. D. Turner
    \end{itemize}

\item International Conference on Atomic Physics, poster presentation, August 2014.
   \begin{itemize}
      \item \textit{Poster title:}
      A Monte Carlo wavefunction method for semiclassical simulations of spin-position entanglement
      \item\textit{Authors:}
      C. J. Billington, C. Watkins, R. P. Anderson, L. D. Turner
    \end{itemize}

\item DPG Spring Meeting of the Atomic, Molecular, Plasma Physics and Quantum Optics Section, poster presentation, March 2013
  \begin{itemize}
      \item \textit{Poster title:}
      Imaging vortices in a Bose--Einstein condensate with tracer particles
      \item\textit{Authors:}
      C. J. Billington, P. T. Starkey, S. P. Johnstone, M. Egorov, K. Helmerson
    \end{itemize}

\item 6th annual Conference on Optics, Atoms and Laser Applications, poster presentation, November 2013.
   \begin{itemize}
      \item \textit{Poster title:}
      Off-resonant four-wave mixing in a Bose--Einstein condensate
      \item\textit{Authors:}
      C. J. Billington, P. T. Starkey, S. P. Johnstone, M. Egorov, K. Helmerson.
    \end{itemize}

\item 5th annual Conference on Optics, Atoms and Laser Applications, contributed talk, December 2012.
   \begin{itemize}
      \item \textit{Talk title:}
      The automatic lab
      \item\textit{Authors:}
      C. J. Billington, P. T. Starkey, S. P. Johnstone, M. Jasperse, R. P. Anderson, L. D. Turner, K. Helmerson.
    \end{itemize}
\item Inaugural Workshop on Quantum-Photonic Hardware, contributed talk, October 2012.
   \begin{itemize}
      \item \textit{Talk title:}
      The automatic lab: a better control and analysis system for quantum science experiments.
      \item\textit{Authors:}
      C. J. Billington, P. T. Starkey, S. P. Johnstone, M. Jasperse, R. P. Anderson, L. D. Turner, K. Helmerson.
    \end{itemize}
\item 4th annual Conference on Optics, Atoms and Laser Applications, poster presentation, December 2011.
   \begin{itemize}
      \item \textit{Poster title:}
      A modular control system for scripted BEC experiments
      \item\textit{Authors:}
      C. J. Billington, P. T. Starkey, S. P. Johnstone, M. Jasperse, R. P. Anderson, L. D. Turner, K. Helmerson.
    \end{itemize}
\item 3rd annual Conference on Optics, Atoms and Laser Applications, poster presentation, December 2010.
   \begin{itemize}
      \item \textit{Poster title:}
      Particle Velocimetry of Bose--Einstein Condensates.
      \item\textit{Authors:}
      C. J. Billington, K. Helmerson.
    \end{itemize}        
\item International Conference on Atomic Physics, poster presentation, July 2010.
   \begin{itemize}
      \item \textit{Poster title:}
      Particle Velocimetry of Bose--Einstein Condensates for Studies of Quantum Turbulence.
      \item\textit{Authors:}
      C. J. Billington, S. P. Johnstone, K. Helmerson.
    \end{itemize}
\end{itemize}


\section*{Publications}

\begin{itemize}

\item S. P. Johnstone, A. J. Groszek, P. T. Starkey, C. J. Billington, T. P. Simula, K. Helmerson, Order from chaos: Observation of large-scale flow from turbulence in a two-dimensional superfluid, \textit{Science} {\bf 364}, 6447 (2019) \doi{10.1126/science.aat5793}

\item F. Salces-Carcoba, C. J. Billington, A. Putra, Y. Yue, S. Sugawa, I. B. Spielman, Equations of state from individual one-dimensional Bose gases, \textit{New Journal of Physics} {\bf 20} 113032 (2018) \doi{10.1088/1367-2630/aaef9b}

\item C.~J.~Billington, State-dependent forces in cold quantum gases, PhD thesis, Monash University (2018) \doi{10.26180/5bd68acaf0696}

\item C. J. Billington, C. J. Watkins, R. P. Anderson, L. D. Turner, A Monte Carlo wavefunction method for semiclassical simulations of spin-position entanglement (2015) \url{https://arxiv.org/abs/1502.06674}

\item P.~T.~Starkey, C.~J.~Billington, S.~P.~Johnstone, M.~Jasperse, R.~P.~Anderson, L.~D.~Turner, K.~Helmerson, A scripted control system for autonomous hardware-timed experiments, \textit{Reviews of Scientific Instruments} {\bf 84}, 085111 (2013) \doi{10.1063/1.4817213}

\item L. M. Bennie, P. T. Starkey, M. Jasperse, C. J. Billington, R. P. Anderson, and L. D. Turner, A versatile high resolution objective for imaging quantum gases, \textit{Optics Express} {\bf 21} 7, pp. 9011-9016 (2013) \doi{10.1364/OE.21.009011}

\item C.~J.~Billington, Particle velocimetry of vortices in Bose--Einstein condensates, Honours thesis, Monash University (2010) \doi{10.13140/RG.2.2.35143.96168}

    
\end{itemize}

\section*{Professional Activities}

\begin{itemize}
\item Co-founder and treasurer, Monash Advanced Science and Science Scholars Society, 2007--2009.
\item Member, Australian Optical Society, 2010--Present.
\item Student Ambassador, Monash Jubilee Open Day 2008.
\end{itemize}

\section*{Honours, Awards, \& Fellowships}

\begin{itemize}
\item High Academic Achievement Award, Monash University, 2007.
\item Highest Academic Performance Award, MTH2140 Real Analysis, Monash University, 2009.
\item Summer Research Scholarship, Australian National University, summer 2008--2009.
\item Highest Academic Performance Award, MTH3360 Fluid Dynamics, Monash University, 2009.
\item Dean's List Fellowship Award, Monash University 2009.
\item Dean's List Fellowship Award, Monash University 2010.
\item J. L. Williams Honours Scholarship, School of Physics, Monash University, 2010.
\item Monash Jubilee Honours Scholarship, Monash University, 2010.
\item Australian Postgraduate Award, Australian government, 2011.
\item J. L. Williams Postgraduate top-up scholarship, School of Physics, Monash University, 2011.
\item Dean's Excellence in Teaching Award, Monash University, 2013.
\end{itemize}

\section*{Software Development}
\begin{description}
\item[SummaryRobot] A Google Wave robot to administer anonymous peer review, developed for and used by students in the second year teaching labs in the School of Physics, Monash University, semester 2 2010.

\item[labscript] A language and compiler for describing precision-timing experiments in physics research laboratories. Developed at Monash University, 2011.

\item[runmanager] A graphical program for producing sequences of \texttt{labscript} experiments with varying input parameters, compiling and running them. Developed at Monash University, 2011.

\item[BLACS] (Better Lab Apparatus Control System), A graphical program for interfacing with hardware in the lab and executing \texttt{labscript} experiments. Developed at Monash University, 2011.

\item[lyse] An analysis program for performing real-time analysis of results from experiments.  Developed at Monash University, 2011.

\item[zprocess] A set of utilties for multiprocess and networked Python programs to communicate and share resources. Developed at Monash University, 2012.

\item[alkali] A Python module for computing details of atomic transitions in hydrogen-like atoms in magnetic fields. Developed at Monash University, 2012.
\end{description}

\medskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
